A numerical study of the solution of X-Mode equations around the hybrid resonance

### 2015-09-14 report_clean_final/TEX/numerics.tex
Correcting typoes as asked by the referee

 \item The C\'ea's lemma applied to the problem (\ref{vf1dcase}); here \mrev{$\mathbf{E}^{\nu}$ is the exact solution, 

@@

The last inequality follows from Lemma \ref{lemma:well_posedness} and is still valid for $\nu\rightarrow 0$.   

@@

 \tilde{E}_x^{\nu}=f_{\nu}(x)\log\rho_{\nu}(x-X_{\nu})+\frac{g_{\nu}(x)}{\rho(x-X_{\nu})},

@@

where $f_{\nu},\; g_{\nu}, \; S_{1}^{\nu}(x)$ are smooth functions, 

@@

Estimate (\ref{eq:cea}) combined with (\ref{eq:interp}) results in, for some $C>0$,

@@

To derive a similar bound on the second derivative of $E_{x}^{\nu}$, we assume that the main contribution to $\|\left(E_{x}^{\nu}\right)''\|_{L^{2}(\Omega)}$
comes from the singular part of $\tilde{E}_{x}^{\nu}$, whose second derivative can be represented in the following form, 
for some functions $F_{\nu,k}(x),\; k=0,..,3,$ uniformly bounded in $x,\; \nu$ in the vicinity of $(x,\nu)=(0,0)$:
\begin{align}
\label{eq:ex_eq1}
 \frac{d^2\tilde{E}_x^{\nu}}{dx^2}=\sum\limits_{k=1}^{3}\frac{F_{\nu,k}(x)}{\left(\rho_{\nu}(x-X_{\nu})\right)^{k}}+F_{\nu,0}(x)\log\rho_{\nu}(x-X_{\nu}).
\end{align}
}
Then there exists $c>0$, s.t. for all sufficiently small $\nu$ 
\bealn
 \left|\frac{d^2E_x^{\nu}}{dx^2}\right|_{L^2}^{2}&\leq c\int\limits_{-L}^{H}\frac{1}{(x^2+\nu^2)^{3}}dx
 % &=c\left.
 %\left(\frac{x}{4(x^2+\nu^2)^2}\nu^{-2}+\frac{3x}{8(x^2+\nu^2)}\nu^{-4}+\frac{3}{8}\nu^{-5}\operatorname{atan}\frac{x}{\nu}\right)\right|_{-L}^{H}
 \leq C\nu^{-5},\; 
\eealn
where $C>0$ does not depend on $\nu$. Plugging this into (\ref{eq:final_est}) we obtain
\ben
 \|E^{\nu}_{x}-E^{\nu,h}_{x}\|_{L^2}\leq C\nu^{-\frac{7}{2}}h^2+C\nu^{-\frac{3}{2}}h.
\een
From this it thus follows that to ensure (\ref{eq:problem1}) $h$ should be chosen as 
\begin{align}
\label{eq:estimate_h}
 h=\alpha_{\epsilon}\nu^{\frac{7}{4}},
\end{align}
where $\alpha_{\epsilon}>0$ depends on $\epsilon$ but does not depend on $\nu$. 
This prediction is very severe and is due to the singular nature of the problem under consideration.

>>>>

 \item \lastrev{The C\'ea lemma} applied to the problem (\ref{vf1dcase}); here \mrev{$\mathbf{E}^{\nu}$ is the exact solution, 

@@

The last inequality follows from Lemma \ref{lemma:well_posedness} and \lastrev{is valid} for $\nu\rightarrow 0$.   

@@

 \tilde{E}_x^{\nu}=f_{\nu}(x)\log\rho_{\nu}(x-X_{\nu})+\frac{g_{\nu}(x)}{\rho\lastrev{_{\nu}}(x-X_{\nu})},

@@

where \lastrev{$f_{\nu},\; g_{\nu}, \; S_{1}^{\nu}$} are smooth functions, 

@@

\lastrev{Let us recall that we defined the function space  $\mathbf{V}=L^{2}(\Omega)\times H^{1}(\Omega)$. }Estimate (\ref{eq:cea}) combined with (\ref{eq:interp}) results in, for some $C>0$. 

@@

To derive a similar bound on the second derivative of $E_{x}^{\nu}$, we assume that the main contribution to $\|\left(E_{x}^{\nu}\right)''\|_{L^{2}(\Omega)}$
comes from the singular part of $\tilde{E}_{x}^{\nu}$, whose second derivative can be represented in the following form, 
for some functions $F_{\nu,k}(x),\; k=0,..,3,$ uniformly bounded in $x,\; \nu$ in the vicinity of $(x,\nu)=(0,0)$:
\begin{align}
\label{eq:ex_eq1}
 \frac{d^2\tilde{E}_x^{\nu}}{dx^2}=\sum\limits_{k=1}^{3}\frac{F_{\nu,k}(x)}{\left(\rho_{\nu}(x-X_{\nu})\right)^{k}}+F_{\nu,0}(x)\log\rho_{\nu}(x-X_{\nu}).
\end{align}
}
Then there exists $c>0$, s.t. for all sufficiently small $\nu$ 
\bealn
 \left\|\frac{d^2E_x^{\nu}}{dx^2}\right\|_{L^2}^{2}&\leq c\int\limits_{-L}^{H}\frac{1}{(x^2+\nu^2)^{3}}dx
 % &=c\left.
 %\left(\frac{x}{4(x^2+\nu^2)^2}\nu^{-2}+\frac{3x}{8(x^2+\nu^2)}\nu^{-4}+\frac{3}{8}\nu^{-5}\operatorname{atan}\frac{x}{\nu}\right)\right|_{-L}^{H}
 \leq C\nu^{-5},\; 
\eealn
where $C>0$ does not depend on $\nu$. Plugging this into (\ref{eq:final_est}) we obtain
\ben
 \|E^{\nu}_{x}-E^{\nu,h}_{x}\|_{L^2}\leq C\nu^{-\frac{7}{2}}h^2+C\nu^{-\frac{3}{2}}h.
\een
From this it thus follows that to ensure (\ref{eq:problem1}) $h$ should be chosen as 
\begin{align}
\label{eq:estimate_h}
 h=\alpha_{\epsilon}\nu^{\frac{7}{4}},
\end{align}
where $\alpha_{\epsilon}>0$ depends on $\epsilon$ but does not depend on $\nu$. 
This prediction is very severe and is due to the singular nature of the problem under consideration.
